Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-18 tex/paper1/paper1.tex
more edits to the paper

There is evidence that these power laws extend to much longer
frequencies than those considered here. \cite{2014AA...563A...8A}
integrate emission over small portions of active regions and the quiet
Sun as seen in the 19.5 nm passband image from the of the SOHO
\cite{1995SoPh..162....1D} Extreme ultraviolet Imaging Telescope (EIT;
\cite{1995SoPh..162..291D}) and show that the resulting time-series
has an approximate \PL\ \Fps.  The frequency range covered by their
study is approximately 0.01 - 1 mHz.

@@

\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
The first contribution to both models $P_{0}$ and $P_{i}$ is a
\PL-like \PS.  It is present in both wavebands studied and in all the
regions, and so parsimony suggests that the mechanism of its creation
is both similar and ubiquitous in all parts of the solar atmosphere.
We hypothesize that the \PL\ \PS\ is due to the sum of a distribution
of a large number of emission events having different amounts of
emission. \cite{2011soca.book.....A} describes how a \PL\ \PS\ may
obtained from such a distribution, and that argument is outlined
below.

>>>>

There is evidence that these power laws extend to much longer
frequencies than those considered here, down to approximately 0.01
mHz. \cite{2014AA...563A...8A} integrate emission over small portions
of active regions and the quiet Sun as seen in the 19.5 nm passband
image from the of the SOHO \cite{1995SoPh..162....1D} Extreme
ultraviolet Imaging Telescope (EIT; \cite{1995SoPh..162..291D}) and
show that the resulting time-series has an approximate \PL\ \Fps\ over
the frequency range 0.01 - 1 mHz.

@@

\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
The first contribution to both models $P_{0}$ and $P_{i}$ is a
\PL-like \PS.  It is present in both wavebands studied and in all the
regions, and so parsimony suggests that the mechanism of its creation
is both similar and ubiquitous in all parts of the solar atmosphere.
Further, \cite{2014AA...563A...8A} show that a \PL\ \PS\ is present in
coronal active region and quiet Sun time-series over the frequency
range 0.01 - 1 mHz, overlapping with the frequency studied in this paper.

We hypothesize that the \PL\ \PS\ is due to the sum of a distribution
of a large number of emission events having different amounts of
emission. \cite{2011soca.book.....A} describes how a \PL\ \PS\ may
obtained from such a distribution, and that argument is outlined
below.
